---
name: Guy Shapira
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD candidate
position: Data Scientist, AI and Bioinformatics researcher
email: guyspersonal@gmail.com
address: " "
website: me.shepp.co
github: shepp-hub
linkedin: guyshapira
headcolor: "303030"
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```



# Employment



```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Director of Computation", "Everly Bio", "2024 - Present", "", 
    list("Developing a novel diagnostic AI model for fertility issues",
         "Responsible for all computation, from bioinformatic analysis to cloud orchestration"
         ),
  "Researcher, Student, Graduate teaching assistant", "Tel Aviv University", "2016 - 2026", "", 
    list("Active academic research, starting as an undergraduate and continuing as a PhD graduate",
         "Credited for 60 scientific publications in 6 years, with over 780 citations (at the time of writing)",
         "Filed two patents for technology transfer based on research findings",
         "Graduate teaching assistant for 4 semesters, 2018-2020"
    ),
  "Statistical advisor", "ExoNavis Therapeutics", "2025 - Present", "", 
    list("Statistical analysis of clinical data, FDA standard complience"),
  "Full-stack developer", "Gotsho Ltd.", "2018 - 2019", "", 
    list("Developed a computational framework for Laboratory Information Management Systems (LIMS)"
    ),
  "Information Technology Developer", "Human Impact", "2014 - 2016", "", 
    list("Family-owned business"
    )
) %>% 
  detailed_entries(role, dates, company, loc, details)
```



# Qualifications



```{r education}
tribble(
  ~ pkg, ~ when, ~ role, ~ details,
  "Doctor of Philosophy", "2021-2026", "Tel Aviv University", "Biomedical Sciences",
  "Master of Science", "2018-2020", "Tel Aviv University", "Biomedical Sciences",
  "Bachelor of Science", "2014-2017", "Tel Aviv University", "Biology"
) %>% 
  brief_entries(glue::glue("\\textbf{<pkg>}: <role> \\newline <details>", .open = "<", .close = ">"), paste0(when, "\\newline"), .protect = FALSE)
```


\newpage

# Achievements & Awards

```{r}
tribble(
  ~ pkg, ~ details, ~ when,
  "Scholarship for Outstanding Research Students", "The Center for Combating Pandemics", "2023",
  "Scholarship for Outstanding Research Students", "Pfizer-Wexler foundation for development and progress", "2023",
  "Fellowship and scholarship", "Edmond J. Safra Center for Bioinformatics", "2022",
  "Academic excellence scholarship", "The Aufzien Family Center for the Prevention and Treatment of Parkinson’s", "2021",
  "Award winning study", "Ziva and Chanoch Finklestein research fund", "2021",
  "Research grant", "The Aufzien Family Center for the Prevention and Treatment of Parkinson's Disease (APPD)", "2020",
  "Research grant", "Adams Super Center for Brain Studies, TAU", "2020"
) %>%
  brief_entries(glue::glue("\\textbf{<pkg>}\\newline <details>", .open = "<", .close = ">"), paste0(when, "\\newline"), .protect = FALSE)
```


# Academic contributions

## Involvement and attendence

- Member of the organizing committee of the Edmond J. Safra Center Biomedical Informatics Entrepreneurs Salon - A bi-monthly forum to promote entrepreneurship at the convergence of biology, medicine, and computing.

- Attended Edmond J. Safra Center for Bioinformatics annual retreat (several years)

- Attended Federation of European Neuroscience Societies (FENS) Forum 2022, Paris, France.

- Attended Human Genome Meeting (HGM) 2020, Perth Australia.

- Attended Computational Genomics Summer Institute (CGSI) 2019 at UCLA.


## Scientific Publications

```{r}
bibliography_entries("publications.bib")
```

